---
title: "Lab 1: Introduction to Quarto"
author: "Aaron Krimer"
date: "09/26/2024"
format:
  html: 
    code-fold: true
editor: source
toc: true
theme: cosmo
embed-resources: true
execute:
  echo: true
  error: true
---

# Part Two: Exploring Quarto Documents

## Specifying Global Execute Options

Execution options specify how the R code in your Quarto document should be
displayed. This [guide](https://quarto.org/docs/computations/execution-options.html)
provides descriptions on the options you can specify in a document's execution.

**Question 1** -- Add your name and the date to the YAML. 

**Question 2** -- Add an `execute` line to you        r YAML that includes the following
options, (1) your source code is always output on the page, and (2) your
document will render even if there are errors.

## Tooth Growth Dataset

```{r}
#| eval: false
#| echo: true
#| label: practicing-running-code

# Load a dataset into the R Environment.
data(ToothGrowth)

# Look at the summary of the variables in the dataset.
summary(ToothGrowth)
```

**Question 3** -- Let's spice this code up a bit. Delete `1 + 1` from the code
chunk and paste in the code provided in the Lab 1 instructions. 

### Check the Data Documentation

**Question 4** -- In your **console** (*not* in the Quarto document), type
`?ToothGrowth` (or alternatively `help(ToothGrowth)`.Use the information that
pops up in the *Help* pane in RStudio to fill in the blanks below. 

*This dataset investigates the effect of _____ on tooth growth in ____.*

*The two supplement delivery methods include OJ (____) and VC (____).*

*`ToothGrowth` is a data frame with ___observations and ____ variables.*

**Question 5** -- *Before* the code chunk, change the "Running the Provided
Code" section header to a header that better describes the contents of this
section (e.g., Tooth Growth Dataset).

## Creating a Plot

**Question 6** -- Replace the `plot(pressure)` code with the code provided in the Lab 1 instructions.

```{r}
#| echo: true
#| label: creating-a-plot
#| layout-ncol: 3

library(tidyverse)

ggplot(data = ToothGrowth, 
       mapping = aes(x = supp, y = len)) +
  geom_boxplot() +
  labs(x = "Supplement", 
       y = "Length of Teeth (mm)", 
       caption = "Figure 1: Boxplot showing the effect of supplement type on tooth length.")

# Second Plot: Boxplot for Dose with a caption
ToothGrowth %>% 
  mutate(dose = as.factor(dose)) %>% 
  ggplot(mapping = aes(x = dose, y = len)) +
  geom_boxplot() +
  labs(x = "Dose of Supplement (mg/day)", 
       y = "Length of Teeth (mm)", 
       caption = "Figure 2: Boxplot showing the effect of supplement dose on tooth length.")
```

Now, run this code chunk! You should see two side-by-side boxplots, one plot
comparing tooth length between the two supplement delivery methods and one plot
comparing tooth length between the three different dosages uses. 

**Question 7** -- Read over the [Quarto documentation on figure options](https://quarto.org/docs/authoring/figures.html#computations)
and add an option (`#|`) to the above code chunk to make the figures print
side-by-side (i.e., in one row) in the rendered HTML file. 

**Question 8** -- Specify in the code chunk options that these boxplots 
should be **center aligned**.

**Question 9** -- Specify a **figure caption** for the boxplots (using a
code-chunk option).

```{r}
library(dplyr)

# Conduct the two-sample independent t-test
t_test_result <- t.test(len ~ supp, data = ToothGrowth, var.equal = FALSE)

# Display the results
t_test_result
```

# Summary of Statistical Analysis on Tooth Lengths by Supplement Type

Conclusion Based on the p-value:
The p-value from the t-test is 0.06063. Since this p-value is slightly above the conventional significance level of 0.05, we do not reject the null hypothesis. This indicates that there is insufficient evidence to conclude that the mean tooth length for the OJ supplement delivery method is different from that of the VC supplement delivery method. However, the p-value is close to the threshold, suggesting that further investigation could be warranted.

Interpretation of the Confidence Interval:
The 95% confidence interval for the difference in means is approximately [−0.171,7.571]. This means we can be 95% confident that the true difference in mean tooth length between the OJ and VC supplements lies within this interval. Since the interval includes zero, it suggests that there is no significant difference in mean tooth lengths between the two groups at the 95% confidence level.




